x---
title: "Exercise 2 - Visa Network Data"
author: "Lisa Reiber"
date: "20 11 2017"
output:
  pdf_document: 
      latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r visa, message=FALSE}
#Get Data
nobel <- read.csv(file = "data/nobel.csv")
#Load Packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, statar) 
```

# Exercise 1a
What is the distribution of females/males by category of the Nobel Prize (absolute and in percentages)?

## Answer 1a:
```{r code 1 answer, message=TRUE}
statar::tab(nobel, gender)
```

\newpage
# Exercise 1b: Please create a visualization using ggplot2.

## Answer 1b:
```{r 1b}
# prep
nobel_plot <- nobel %>% filter(gender != "org", category != "") 
 
# 1. Horizontal Bar Chart, Categories by Gender (Proportion)
nobel_plot %>% 
      ggplot(aes(category, fill = gender)) +
            geom_bar(alpha = 4/5, position = position_fill(reverse = TRUE)) +
            coord_flip() +
            scale_y_continuous(labels = scales::percent) +
            labs(title = "Proportion of Gender within Nobel Prize Categories",
                 y = "",
                 x="")
```
\newpage
```{r}
# visualize inequality
# 2. Vertical Bar Chart, Gender by Categories (Count)
nobel_plot %>% 
      ggplot(aes(gender, fill = category) ) +
      geom_bar(alpha = 3/5, position = "stack") +
      theme_minimal() +
      labs( title = "Number of Nobel Prize Categories within Gender",
            y= "Number of Nobel Prizes")
```
\newpage
```{r}
# visualize both distributions, hide inequality/ highlight distrib of categ.
# 3. Vertical Bar Chart, Gender by Categories (Proportion)
nobel_plot %>% 
      ggplot(aes(gender, fill = category) ) +
      geom_bar(alpha = 4/5, position = "fill") +
      theme_light() +
      scale_y_continuous(labels = scales::percent) +
      labs( title = "Proportion of Nobel Prize Categories within Gender",
            y = "")
```

\newpage
```{r }
# 4. boxplot number of prizes
nobel_plot %>%
      group_by(gender, category) %>% 
      summarize(prizes = n()) %>% 
      ggplot(aes(x= gender, y= prizes, colour = category)) +
      geom_boxplot()

# 5.. hahaha
nobel_plot %>% 
      ggplot(aes(category, fill = gender)) +
            geom_bar(alpha = 4/5, position = position_fill()) +
            coord_polar() +
            labs(title = "Proportion of Gender within Nobel Prize Categories",
                 y = "",
                 x="")
```

\newpage
```{r}
# 5. Nobel Prizes by year over gender
ggplot(data = nobel_plot, mapping = aes(x = year, fill = category)) +
      geom_histogram(position = "stack", binwidth = 5) +
      facet_wrap(c("gender"), scales = , dir = "v") +
      scale_x_continuous(breaks = seq(1900, 2010, 10), limits = c(1900, 2020)) +
      labs(title ="Number of Nobel Prizes from 1901 to 2017 by Gender ",
           y= "Number of Nobel Prizes", x = "")
```

\newpage
# Exercise 2:
How does the age distribution of Nobel Prize Laureates look like (their age when they received the prize)? Again, please visualize your result.


## Anser 2:
```{r 2b}
#prep
library(stringr)
nobel_plot <- nobel_plot %>% 
      mutate(born = strtoi(str_extract_all(born, "[:digit:]{4}"))) %>% 
      filter(born > 0) %>% 
      mutate(age_win = year - born) 

# histogram 
nobel_plot %>% 
      ggplot(aes(x= age_win, y= ..density..)) +
      geom_histogram(binwidth = 1)  +
      labs(title ="Distribution of Nobel Prize Winners' Age",
          x = "Age in Years")

# boxplot
nobel_plot %>%
      ggplot(aes(x= gender, y= age_win, fill = category)) +
      geom_boxplot() +
      labs(title ="Distribution of Nobel Prize Winners' Age by Categories and Gender",
           y="Age in Years", x = "")

```

